Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-05-21 Scripts/Initial_Analysis.Rmd
updated analysis with correct paths and functions

#### Project's Library
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt" # for estimating distances between points
)

@@

EEZ_CellID <- my_path("G", extra_path = "Spatial/DBEM", name="EEZ_CellID.xlsx", read = TRUE) %>% 
  clean_names()

colnames(EEZ_CellID) <- c("eezid","index")

@@

# Read transboundary species database from Palacios-Abrantes et al 2020 (FishForVisa)
Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names()

@@

EstPropChange <- function(taxon_key,
                          year,
                          hist_y,
                          data_type = "Catch",
                          ensamble_list, # expects a list of ensambles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensambles
  Spp_Dist <- bind_rows(
    lapply(
      ensamble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

  #Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensamble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      year,
      ensamble
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      Name=eez_neighbour,
      eez_name,
      year,
      ensamble
    )

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensamble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensamble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # Ensamble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("temporal_mean"),
                 c(ensamble_mean=mean,
                   ensamble_sd=sd),
                 na.rm=T
    )

@@

  # Or return a df
  return(Per_Ghange_D)
}

# EstPropChange(taxon_key = 600004,
#               year = year_df,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensamble_list = ensamble_list,
#               path = path,
#               neighbours = neighbours)

@@

```{r Emerging_control_panel, eval = T, echo = F}

@@

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- read_csv(paste(data_path,"Spatial/sau_index_code.csv",sep=""))

# Neighbour list and their respective id (see chunk 3)
Neighbours <- read_csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- read_csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names() %>% 
  select(-x1)

@@

# List of ensamble members
ensamble_list <- seq(102,103,1) # for testing
# ensamble_list <- seq(102,111,1)

@@

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

@@

This rutine estimates the time (e.g. year) in which the changes in stock share ratio is more likely to happen based on historical variations (e.g. model noise) and future trends (e.g signal). This result uses teh average of the 10 ensamble members

@@

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensamble, 
                         path,
                         Neighbours,
                         eez_centroid){

  # ----------------- #
  # Get model data from spps for one ensamble
  #  ---------------- #

  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensamble = ensamble,
    path = path
  )

@@

  #### Creates a data to control computational time
  if(file.exists("~/Desktop/spp_df.csv") == FALSE){
    spp_df <- tibble() %>% 
      write_csv(.,
                "~/Desktop/spp_df.csv")
  }

  suppressMessages(
    spp_df <- read_csv("~/Desktop/spp_df.csv")
  )
  spp_df <- tibble(taxon_key,
                   ensamble) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              "~/Desktop/spp_df.csv")

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensamble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x) %>% 
        # Estimate distances between spp centroid and EEZ centroid
        mutate(
          distance = geodist(longitude, # eez longitude
                             latitude,  # eez latitude
                             lon,  # species longitude
                             lat, # species latitude
                             units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensamble,year,distance)

@@

GetCentroids(taxon_key = 600004,
             year = year_df,
             # data_type = data,
             ensamble = 102,
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )

@@

  # Historical mean and sd of distance
  historical <- Centroids_id %>%
    filter(year <= Hist_y) %>% 
    ungroup() %>%
    group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
    summarise_at(vars("distance"),
                 c(hd_temp_mean=mean,
                   hd_temp_sd=sd)
    )

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensamble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup()

@@

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensamble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

  # Average of 10 years mean of ensamble members results
  mean_sd_index <- Partial %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensamble_sd=sd)
    )

  # Estimate noice from ensamble members
  historic_sd <- mean_sd_index %>% 
    filter(year < Hist_y) %>% 
    group_by(taxon_key) %>% 
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd)
    )

@@

This is the last function of the emerging year evaluation. It was made so we could run the analysis per each species. The function function simply runs the functions `GetCentroids` by ensabmble member and then `TransIndex` by pairing EEZ. Thus, with this function we run the whole set by species * paired EEZ * ten ensamble members.

@@

GetTransIndex <- function(taxon_key,
                            year,
                          Hist_y,
                            data_type = "Catch",
                            path,
                            ensamble_list,
                            Neighbours,
                            eez_centroid){

    # First step
    # Call Get centroids fucntion for centroids data per ensamble
    Step_one <- bind_rows(
      lapply(ensamble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = data_type,
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensamble_list = ensamble_list[1:2],
  #   year = year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   path = path,
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

  # spp_list <- c(600004, 600245)
  # 
  #  test <- bind_rows(
  #   lapply(spp_list,
  #          GetTransIndex,
  #          year = year,
  #          data_type = "Catch",
  #          path = path,
  #          Neighbours = Neighbours,
  #          eez_centroid = eez_centroid,
  #          ensamble_list = ensamble_list
  #   )
  # )
  #

@@

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- read_csv(paste(data_path,"Spatial/sau_index_code.csv",sep=""))

# EEZ list and their centroid of distribution (see chunk 3)
eez_centroid <- read.csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""), header=TRUE)

# Neighbour list and their respective id (see chunk 3)
Neighbours <- read.csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names()

@@

# List of ensamble members
ensamble_list <- seq(102,103,1) # for testing
# ensamble_list <- seq(102,111,1)

@@

suppressMessages(
  suppressWarnings(
    Emerging_result <- bind_rows(
      mclapply(spp_list[1],
               GetTransIndex,
               year = year_df,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensamble_list = ensamble_list,
               path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )
    }

@@

Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

TransIndex <- function(Spp,year, data_type = "Catch",ensamble_list,path,Neighbours,eez_centroid){

@@

  # Get model data from spps
  Spp_Dist <- bind_rows(
    lapply(
      ensamble_list,
      dbem_import,
      taxon_key = Spp,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensamble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x)

      # Estimate distances between spp centroid and EEZ centroid
      Distance_Data <- Centroids %>%
        rename(
          catch_lon = lon,
          catch_lat = lat,
          eez_lon = longitude,
          eez_lat= latitude
        ) %>% 
        # Estimate the distance between centriods
        mutate(
          distance = geodist(eez_lon, eez_lat, catch_lon, catch_lat, units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensamble,year,distance)

      # Historical mean and sd of distance
      historical <- Distance_Data %>%
        filter(year <= 2000) %>%
        ungroup() %>%
        group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
        summarise_at(vars("distance"),
                     c(hd_temp_mean=mean,
                       hd_temp_sd=sd)
        )

@@

      # Transboundary Index
      Trans_index <- Distance_Data %>% 
        left_join(historical,
                  by = c("taxon_key","eez_name","ensamble","neighbour_id")
        ) %>%
        # Re arrenging table for mutate
        gather("variable","value",distance:hd_temp_sd) %>%
        ungroup()

      Partial <- Trans_index %>% 
        mutate(
          names = ifelse(eez_name ==Sub_EEZ_centroid$eez_name[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
        ) %>%
        select(-eez_name,-variable) %>%
        spread(names,value) %>% 
        # mutate index
        mutate(
          trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
        ) %>% 
        group_by(taxon_key,ensamble,neighbour_id) %>% 
        mutate(RMean = rollmean(x = trans_index, 
                                10, 
                                align = "right", 
                                fill = trans_index)
        ) %>% 
        filter(year > 1960) %>% 
        select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

      # Average of 10 years mean of ensamble members results
      mean_sd_index <- Partial %>% 
        group_by(taxon_key,year,neighbour_id) %>% 
        summarise_at(vars("RMean"),
                     c(trend=mean,
                       ensamble_sd=sd)
        )

      # Estimate noice from ensamble members
      historic_sd <- mean_sd_index %>% 
        filter(year < 2000) %>% 
        group_by(taxon_key) %>% 
        summarise_at(vars("trend"),
                     c(hist_mean=mean,
                       noise=sd)
        )

@@

#  #One spp works 
# suppressMessages(
# TransIndex(Spp = 600006,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours = Neighbours,
#              eez_centroid)
# Multiple spp

# spp_list <- c(600004,
#               600005,
#               600245,
#               600006
#               )
# 
# suppressMessages(
#   suppressWarnings(
#     Test <- bind_rows(
#       lapply(spp_list,
#              TransIndex,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours,
#              eez_centroid
#       )
#     )
#   )
# )

>>>>

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt" # for estimating distances between points
)

@@

EEZ_CellID <- my_path("G", extra_path = "Spatial/DBEM", name="EEZ_CellID.xlsx", read = TRUE) %>% 
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

@@

# Read transboundary species database from Palacios-Abrantes et al 2020 (FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE)

@@

EstPropChange <- function(taxon_key,
                          year,
                          hist_y,
                          data_type = "Catch",
                          ensemble_list, # expects a list of ensembles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

  #Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensemble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      year,
      ensemble
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      Name=eez_neighbour,
      eez_name,
      year,
      ensemble
    )

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensemble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensemble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # ensemble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("temporal_mean"),
                 c(ensemble_mean=mean,
                   ensemble_sd=sd),
                 na.rm=T
    )

@@

  # Or return a df
  # return(Per_Ghange_D)
}

# EstPropChange(taxon_key = 600004,
#               year = year_df,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensemble_list = ensemble_list,
#               path = path,
#               neighbours = neighbours)

@@

```{r Proportion_control_panel, eval = T, echo = F}

@@

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- my_path("G", extra_path = "Spatial/SAU/", name="sau_index_code.csv", read = TRUE)

# Neighbour list and their respective id (see chunk 3)
Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE)

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE) %>% 
  clean_names() %>% 
  select(-x1)

@@

# List of ensemble members
ensemble_list <- seq(102,103,1) # for testing
# ensemble_list <- seq(102,111,1)

#  List os species
spp_list <- unique(Transboundary_spp$taxon_key)

@@

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensemble_list = ensemble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

@@

This rutine estimates the time (e.g. year) in which the changes in stock share ratio is more likely to happen based on historical variations (e.g. model noise) and future trends (e.g signal). This result uses teh average of the 10 ensemble members

@@

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensemble, 
                         # path,
                         Neighbours,
                         eez_centroid){

  # ----------------- #
  # Get model data from spps for one ensemble
  #  ---------------- #

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble,
    path = my_path("D",extra_path = "/DBEM")
  )

@@

  #### Creates a data to control computational time (lol!)
    if(file.exists(paste(my_path("R"),"spp_df.csv",sep="")) == FALSE){
    spp_df <- tibble() %>% 
      write_csv(.,
                paste(my_path("R"),"spp_df.csv",sep=""))
  }

  suppressMessages(
    spp_df <- my_path("R",name="spp_df.csv",read = TRUE)
  )
  spp_df <- tibble(taxon_key,
                   ensemble) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              paste(my_path("R"),"spp_df.csv",sep=""))

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensemble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x) %>% 
        # Estimate distances between spp centroid and EEZ centroid
        mutate(
          distance = geodist(longitude, # eez longitude
                             latitude,  # eez latitude
                             lon,  # species longitude
                             lat, # species latitude
                             units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensemble,year,distance)

@@

# Test function

# Test_centroids <- GetCentroids(taxon_key = 600004,
#              year = year_df$year,
#              # data_type = data,
#              ensemble = 102,
#              # path = path,
#              Neighbours = Neighbours,
#              eez_centroid = eez_centroid
#              )
# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

  # Historical mean and sd of distance
  historical <- Centroids_id %>%
    filter(year <= Hist_y) %>% 
    ungroup() %>%
    group_by(taxon_key,ensemble,eez_name,neighbour_id) %>%
    summarise_at(vars("distance"),
                 c(hd_temp_mean=mean,
                   hd_temp_sd=sd)
    )

@@

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensemble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup()

@@

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- Partial %>% 
    group_by(taxon_key,year,neighbour_id) %>% 
    summarise_at(vars("RMean"),
                 c(trend=mean,
                   ensemble_sd=sd)
    )

  # Estimate noice from ensemble members
  historic_sd <- Partial %>% 
    filter(year < Hist_y) %>% 
    group_by(taxon_key) %>% 
    summarise_at(vars("RMean"),
                 c(hist_mean=mean,
                   noise=sd)
    )

  # Plot the result, bruh
  # For testing
  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    ) +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    ggsave("plot_example.jpg",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

This is the last function of the emerging year evaluation. It was made so we could run the analysis per each species. The function function simply runs the functions `GetCentroids` by ensabmble member and then `TransIndex` by pairing EEZ. Thus, with this function we run the whole set by species * paired EEZ * ten ensemble members.

@@

GetTransIndex <- function(taxon_key,
                            year,
                          Hist_y,
                            data_type = "Catch",
                            path,
                            ensemble_list,
                            Neighbours,
                            eez_centroid){

    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensemble_list = ensemble_list[1:2],
  #   year = year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

  # spp_list <- c(600004, 600245)
  # 
  #  test <- bind_rows(
  #   lapply(spp_list,
  #          GetTransIndex,
  #          year = year,
  #          data_type = "Catch",
  #          path = path,
  #          Neighbours = Neighbours,
  #          eez_centroid = eez_centroid,
  #          ensemble_list = ensemble_list
  #   )
  # )
  #

@@

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- my_path("G", extra_path = "Spatial/SAU/", name="sau_index_code.csv", read = TRUE)

# EEZ list and their centroid of distribution (see chunk 3)
eez_centroid <- my_path("D", extra_path = "Spatial/", name="eez_centroids.csv", read = TRUE)

# Neighbour list and their respective id (see chunk 3)
Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE)

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE) %>% 
  clean_names()

@@

# Data path
# path = DBEM_path

# List of ensemble members
ensemble_list <- seq(102,103,1) # for testing
# ensemble_list <- seq(102,111,1)

@@

suppressMessages(
  suppressWarnings(
    Emerging_result <- bind_rows(
      mclapply(spp_list[1],
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensemble_list = ensemble_list,
               # path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )
    }

@@

Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE) %>% 
  clean_names()

@@

TransIndex <- function(Spp,year, data_type = "Catch",ensemble_list,path,Neighbours,eez_centroid){

@@

  # Get model data from spps
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      dbem_import,
      taxon_key = Spp,
      year = year,
      data_type = data_type,
      path = path
    )
  )

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensemble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x)

      # Estimate distances between spp centroid and EEZ centroid
      Distance_Data <- Centroids %>%
        rename(
          catch_lon = lon,
          catch_lat = lat,
          eez_lon = longitude,
          eez_lat= latitude
        ) %>% 
        # Estimate the distance between centriods
        mutate(
          distance = geodist(eez_lon, eez_lat, catch_lon, catch_lat, units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensemble,year,distance)

      # Historical mean and sd of distance
      historical <- Distance_Data %>%
        filter(year <= 2000) %>%
        ungroup() %>%
        group_by(taxon_key,ensemble,eez_name,neighbour_id) %>%
        summarise_at(vars("distance"),
                     c(hd_temp_mean=mean,
                       hd_temp_sd=sd)
        )

@@

      # Transboundary Index
      Trans_index <- Distance_Data %>% 
        left_join(historical,
                  by = c("taxon_key","eez_name","ensemble","neighbour_id")
        ) %>%
        # Re arrenging table for mutate
        gather("variable","value",distance:hd_temp_sd) %>%
        ungroup()

      Partial <- Trans_index %>% 
        mutate(
          names = ifelse(eez_name ==Sub_EEZ_centroid$eez_name[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
        ) %>%
        select(-eez_name,-variable) %>%
        spread(names,value) %>% 
        # mutate index
        mutate(
          trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
        ) %>% 
        group_by(taxon_key,ensemble,neighbour_id) %>% 
        mutate(RMean = rollmean(x = trans_index, 
                                10, 
                                align = "right", 
                                fill = trans_index)
        ) %>% 
        filter(year > 1960) %>% 
        select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

      # Average of 10 years mean of ensemble members results
      mean_sd_index <- Partial %>% 
        group_by(taxon_key,year,neighbour_id) %>% 
        summarise_at(vars("RMean"),
                     c(trend=mean,
                       ensemble_sd=sd)
        )

      # Estimate noice from ensemble members
      historic_sd <- mean_sd_index %>% 
        filter(year < 2000) %>% 
        group_by(taxon_key) %>% 
        summarise_at(vars("trend"),
                     c(hist_mean=mean,
                       noise=sd)
        )

@@

#  #One spp works 
# suppressMessages(
# TransIndex(Spp = 600006,
#              year,
#              data_type = "Catch",
#              ensemble_list,
#              path,
#              Neighbours = Neighbours,
#              eez_centroid)
# Multiple spp

# spp_list <- c(600004,
#               600005,
#               600245,
#               600006
#               )
# 
# suppressMessages(
#   suppressWarnings(
#     Test <- bind_rows(
#       lapply(spp_list,
#              TransIndex,
#              year,
#              data_type = "Catch",
#              ensemble_list,
#              path,
#              Neighbours,
#              eez_centroid
#       )
#     )
#   )
# )
